### 2020-10-14 priority-cp.tex
Simon's comments.

\subsubsection*{Types}
Types $\pcp{\ty{A}}$, $\pcp{\ty{B}}$, $\pcp{\ty{C}}$ in PCP are based on classical linear logic propositions, and are defined by the following grammar:
\[
  \usingnamespace{pcp}
  \begin{array}{lcl}
    \ty{A}, \ty{B}, \ty{C}
    & \coloneqq & \ty{\tytens[\cs{o}]{A}{B}}
      \sep        \ty{\typarr[\cs{o}]{A}{B}}
      \sep        \ty{\tyone[\cs{o}]}
      \sep        \ty{\tybot[\cs{o}]}
      \sep        \ty{\typlus[\cs{o}]{A}{B}}
      \sep        \ty{\tywith[\cs{o}]{A}{B}}
      \sep        \ty{\tynil[\cs{o}]}
      \sep        \ty{\tytop[\cs{o}]}
  \end{array}
\]
Each connective is annotated with a priority $\cs{o}\in\mathbb{N}$.
The types $\pcp{\ty{\tytens[\cs{o}]{A}{B}}}$ and $\pcp{\ty{\typarr[\cs{o}]{A}{B}}}$ type the endpoints of a channel over which we send or receive a channel of type $\pcp{\ty{A}}$, and then proceed as type $\pcp{\ty{B}}$. The types $\pcp{\ty{\tyone[\cs{o}]}}$ and $\pcp{\ty{{\tybot}[\cs{o}]}}$ type the endpoints of a channel whose session has terminated, and over which we send or receive a \emph{ping} before closing the channel. These two types act as units for $\pcp{\ty{\tytens[\cs{o}]{A}{B}}}$ and $\pcp{\ty{\typarr[\cs{o}]{A}{B}}}$, respectively.

@@

\subsubsection*{Environments}
Typing environments $\pcp{\ty{\Gamma}}$, $\pcp{\ty{\Delta}}$ associate names to types. Environments are linear, so two environments can only be combined as $\pcp{\ty{\Gamma}}, \pcp{\ty{\Delta}}$ if their names are distinct, \ie $\pcp{\fv(\ty{\Gamma})\cap\fv(\ty{\Delta})=\varnothing}$.
\[
  \usingnamespace{pcp}
  \begin{array}{lcl}
    \ty{\Gamma}, \ty{\Delta}
    & \coloneqq & \ty{\emptyenv}
      \sep        \ty{\Gamma}, \tmty{x}{A}
  \end{array}
\]

@@

\subsubsection*{Terms}
We let $\pcp{\tm{P}}$, $\pcp{\tm{Q}}$ range over processes, produced by the following grammar.
\[
  \usingnamespace{pcp}
  \begin{array}[t]{lcl}
    \tm{P}, \tm{Q}
    & \coloneqq & \tm{\link{x}{y}}
           \sep   \tm{\res{x}{y}{P}}
           \sep   \tm{(\ppar{P}{Q})}
           \sep   \tm{\halt}
    \\   & \sep & \tm{\send{x}{y}{P}}
           \sep   \tm{\close{x}{P}}
           \sep   \tm{\recv{x}{y}{P}}
           \sep   \tm{\wait{x}{P}}
    \\   & \sep & \tm{\inl{x}{P}}
           \sep   \tm{\inr{x}{P}}
           \sep   \tm{\offer{x}{P}{Q}}
           \sep   \tm{\absurd{x}}
  \end{array}
\]
The process $\pcp{\tm{\link{x}{y}}}$ links endpoints $\pcp{\tm{x}}$ and $\pcp{\tm{y}}$ and forwards communication from one to the other. $\pcp{\tm{\res{x}{y}{P}}}$, $\pcp{\tm{(\ppar{P}{Q})}}$ and $\pcp{\tm{\halt}}$ denote respectively the restriction processes where channel endpoints $\pcp{\tm{x}}$ and $\pcp{\tm{y}}$ are bound together and with scope $\pcp{\tm{P}}$, the parallel composition of processes $\pcp{\tm{P}}$ and $\pcp{\tm{Q}}$ and the terminated process.

Processes $\pcp{\tm{\send{x}{y}{P}}}$ and $\pcp{\tm{\recv{x}{y}{P}}}$ send or receive over channel $\pcp{\tm{x}}$ a value $\pcp{\tm{y}}$ and proceed as process $\pcp{\tm{P}}$. $\pcp{\tm{\close{x}{P}}}$ and $\pcp{\tm{\wait{x}{P}}}$ send and receive an empty value -- denoting the closure of channel $\pcp{\tm{x}}$, and continue as $\pcp{\tm{P}}$.

Processes $\pcp{\tm{\inl{x}{P}}}$ and $\pcp{\tm{\inr{x}{P}}}$ make a left and right choice, respectively and proceed as process $\pcp{\tm{P}}$. $\pcp{\tm{\offer{x}{P}{Q}}}$ dually offers both left and right branches, with continuations $\pcp{\tm{P}}$ and $\pcp{\tm{Q}}$. $\pcp{\tm{\absurd{x}}}$ denotes the empty offer.

@@

\subsubsection*{Operational Semantics}
The operational semantics for PCP, given in \cref{fig:pcp-operational-semantics}, is defined as a reduction relation $\pcp{\red}$ on processes (bottom) and uses structural congruence (top). Each of the axioms of structural congruence corresponds to the axiom of the same name for PGV.

@@

\subsubsection*{Translation}
The translation on types from PCP to PGV, $\ty{\cpgvT{\cdot}}$, is:
\[
  \begin{array}{lcl}
    \ty{\cpgvT{\pcp{\tytens[\cs{o}]{A}{B}}}}
    & = & \pgv{\ty{\tysend[\cs{o}]{\co{\cpgvT{A}}}{\cpgvT{B}}}}
    \\
    \ty{\cpgvT{\pcp{\typlus[\cs{o}]{A}{B}}}}
    & = & \pgv{\ty{\tyselect[\cs{o}]{\cpgvT{A}}{\cpgvT{B}}}}
  \end{array}
  \;
  \begin{array}{lcl}
    \ty{\cpgvT{\pcp{\tyone[\cs{o}]}}}
    & = & \ty{\pgv{\tyends[\cs{o}]}}
    \\
    \ty{\cpgvT{\pcp{\tynil[\cs{o}]}}}
    & = & \pgv{\ty{\tyselectemp[\cs{o}]}}
  \end{array}
  \;
  \begin{array}{lcl}
    \ty{\cpgvT{\pcp{\typarr[\cs{o}]{A}{B}}}}
    & = & \pgv{\ty{\tyrecv[\cs{o}]{\cpgvT{A}}{\cpgvT{B}}}}
    \\
    \ty{\cpgvT{\pcp{\tywith[\cs{o}]{A}{B}}}}
    & = & \pgv{\ty{\tyoffer[\cs{o}]{\cpgvT{A}}{\cpgvT{B}}}}
  \end{array}
  \;
  \begin{array}{lcl}
    \ty{\cpgvT{\pcp{\tybot[\cs{o}]}}}
    & = & \ty{\pgv{\tyendr[\cs{o}]}}
    \\
    \ty{\cpgvT{\pcp{\tytop[\cs{o}]}}}
    & = & \pgv{\ty{\tyofferemp[\cs{o}]}}
  \end{array}
\]
There are two separate translations on processes. The first, $\tm{\cpgvC{\cdot}}$, translates processes to \emph{configurations}. It translates as much as possible of the process to the corresponding configuration constructs. Once it hits the first action, it switches to the second translation, $\tm{\cpgvM{\cdot}}$, which translates processes to \emph{terms}:
\[
  \begin{array}{lcl}
    \pcp{\tm{\cpgvC{\res{x}{y}{P}}}}
    & = & \pgv{\tm{\res{x}{y}{\cpgvC{P}}}} \\
    \pcp{\tm{\cpgvC{\ppar{P}{Q}}}}
    & = & \pgv{\tm{\ppar{\cpgvC{P}}{\cpgvC{Q}}}} \\
    \pcp{\tm{\cpgvC{\send{x}{y}{P}}}}
    & = & \pgv{\tm{\res{y}{z}{(\child\;\letbind{x}{\send\;\pair{z}{x}}{\cpgvM{P}})}}} \\
    \pcp{\tm{\cpgvC{\inl{x}{P}}}}
    & = & \pgv{\tm{\res{y}{z}{(\child\;\letbind{x}{\andthen{\close\;(\send\;\pair{\inl{y}}{x})}{z}}{\cpgvM{P}})}}} \\
    \pcp{\tm{\cpgvC{\inr{x}{P}}}}
    & = & \pgv{\tm{\res{y}{z}{(\child\;\letbind{x}{\andthen{\close\;(\send\;\pair{\inr{y}}{x})}{z}}{\cpgvM{P}})}}} \\
    \pcp{\tm{\cpgvC{P}}}
    & = & \pgv{\tm{\child{\cpgvM{P}}}},\hfill\text{if none of the above apply}\\
    \\
    \pcp{\tm{\cpgvM{\link{x}{y}}}}
    & = & \pgv{\tm{\link\;{\pair{x}{y}}}} \\
    \pcp{\tm{\cpgvM{\res{x}{y}{P}}}}
    & = & \pgv{\tm{\letpair{x}{y}{\new}{\cpgvM{P}}}} \\
    \pcp{\tm{\cpgvM{\ppar{P}{Q}}}}
    & = & \pgv{\tm{\andthen{\spawn\;{(\lambda\unit.\cpgvM{P})}}{\cpgvM{Q}}}} \\
    \pcp{\tm{\cpgvM{\halt}}}
    & = & \pgv{\tm{\unit}} \\
    \pcp{\tm{\cpgvM{\close{x}{P}}}}
    & = & \pgv{\tm{\andthen{\close\;{x}}{\cpgvM{P}}}} \\
    \pcp{\tm{\cpgvM{\wait{x}{P}}}}
    & = & \pgv{\tm{\andthen{\wait\;{x}}{\cpgvM{P}}}} \\
    \pcp{\tm{\cpgvM{\send{x}{y}{P}}}}
    & = & \pgv{\tm{\letpair{y}{z}{\new}{\letbind{x}{\send\;{\pair{z}{x}}}{\cpgvM{P}}}}} \\
    \pcp{\tm{\cpgvM{\recv{x}{y}{P}}}}
    & = & \pgv{\tm{\letpair{y}{x}{\recv\;{x}}{\cpgvM{P}}}} \\
    \pcp{\tm{\cpgvM{\inl{x}{P}}}}
    & = & \pgv{\tm{\letbind{x}{\select{\labinl}\;{x}}{\cpgvM{P}}}} \\
    \pcp{\tm{\cpgvM{\inr{x}{P}}}}
    & = & \pgv{\tm{\letbind{x}{\select{\labinr}\;{x}}{\cpgvM{P}}}} \\
    \multicolumn{3}{l}{\pcp{\tm{\cpgvM{\offer{x}{\cpgvM{P}}{\cpgvM{Q}}}}}} \\
    & = & \pgv{\tm{\offer{x}{x}{\cpgvM{P}}{x}{\cpgvM{Q}}}} \\
    \pcp{\tm{\cpgvM{\absurd{x}}}}
    & = & \pgv{\tm{\offeremp{x}}}
  \end{array}
\]
The third, fourth, and fifth cases for $\tm{\cpgvC{\cdot}}$ translate the $\nu$-binders implicit in the encoding of bound sending to configuration constructs, which is required for completeness of the operational correspondence.
Typing environments are translated pointwise, and sequents $\pcp{\seq{P}{\ty{\Gamma}}}$ are translated as $\pgv{\cseq[\child]{\ty{\cpgvT{\ty{\Gamma}}}}{\cpgvC{P}}}$.

\subsubsection*{Example: Milner's Cyclic Scheduler}\label{sec:pcp-example}
We illustrate our translation by giving the PCP version of the cyclic scheduler in~\cref{sec:pgv-example}. We implement the scheduler as follows, using $\pcp{\tm{\prod_{i}P_i}}$ to denote the parallel composition of the processes $\pcp{\tm{P_i}}$, and $\pcp{\plug{P}{Q}}$ to denote the plugging of $\pcp{\tm{Q}}$ in the one-hole process context $\pcp{\tm{P}}$:
\[
  \usingnamespace{pcp}
  \begin{array}{lrlr}
    \tm{\sched}
    & \defeq & \tm{\res{a_1}{a'_1}{\dots{\res{a_n}{a'_n}{}}}}
               \tm{\res{b_1}{b'_1}{\dots{\res{b_n}{b'_n}{}}}}
               \tm{\res{c_1}{c'_1}{\dots{\res{c_n}{c'_n}{}}}}
               \tm{\res{d}{d'}{}}
    \\ &     & \tm{(
               \ppar{\proc1}{\agent1}
               \parallel
               \prod_{2\leq{i}\leq{n}}(\ppar{\proc{i}}{\wait{c'_{i-1}}{\agent{i}}})
               )}
    \\
    \tm{\agent1}
    & \defeq & \tm{\close{a_i}{\wait{b_i}{\close{c_i}{\wait{c'_n}{\close{d}{\halt}}}}}}
    \\
    \tm{\agent{i}}
    & \defeq & \tm{\close{a_i}{\wait{b_i}{\close{c_i}{\halt}}}}
    \\
    \tm{\proc{i}}
    & \defeq & \tm{\wait{a'_i}{\plug{P_i}{\close{b'_i}{Q_i}}}}
  \end{array}
\]
The translation of $\pcp{\sched}$ is exactly $\pgv{sched}$ where all processes are child processes.

\subsubsection*{Type preservation}
The translations $\tm{\cpgvC{\cdot}}$ and $\tm{\cpgvM{\cdot}}$ preserve typing along $\ty{\cpgvT{\cdot}}$:
\begin{restatablelemma}{lempcptopgvtermspreservation}[Preservation, $\cpgvM{\cdot}$]
  \label{lem:pcp-to-pgv-terms-preservation}
  \hfill\\%newline before theorem statement
  If $\pcp{\seq{P}{\ty{\Gamma}}}$ in PCP,
  then $\pgv{\tseq[\cs{p}]{\ty{\cpgvT{\Gamma}}}{\cpgvM{P}}{\tyunit}}$ in PGV.
\end{restatablelemma}
\begin{proof}
  By induction on the derivation of $\pcp{\seq{P}{\ty{\Gamma}}}$.
  Details in \cref{prf:lem-pcp-to-pgv-terms-preservation}.
\end{proof}
\begin{restatabletheorem}{thmpcptopgvconfspreservation}[Preservation, $\cpgvC{\cdot}$]
  \label{thm:pcp-to-pgv-confs-preservation}
  \hfill\\%newline before theorem statement
  If $\pcp{\seq{P}{\ty{\Gamma}}}$ in PCP,
  then $\pgv{\cseq[\child]{\ty{\cpgvT{\Gamma}}}{\cpgvC{P}}}$ in PGV.
\end{restatabletheorem}
\begin{proof}
  By induction on the derivation of $\pcp{\seq{P}{\ty{\Gamma}}}$.
  Details in \cref{prf:lem-pcp-to-pgv-terms-preservation}.
\end{proof}

@@

\begin{restatabletheorem}{thmpcptopgvoperationalcorrespondencesoundness}%
  [Operational Correspondence, Soundness, $\cpgvC{\cdot}$]
  \label{thm:pcp-to-pgv-operational-correspondence-soundness}
  \hfill\\%newline before theorem statement
  If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pgv{\tm{\cpgvC{P}}\cred\tm{\conf{C}}}$,
  there exists a $\tm{Q}$ such that $\pcp{\tm{P}\red^+\tm{Q}}$ and $\pgv{\tm{\conf{C}}\cred^\star\tm{\cpgvC{Q}}}$
\end{restatabletheorem}
\begin{proof}
  By induction on the derivation of $\pgv{\tm{\cpgvC{P}}\cred\tm{\conf{C}}}$.
  Details in \cref{prf:thm-pcp-to-pgv-operational-correspondence-soundness}.
\end{proof}

@@

>>>>

\subsubsection*{Example}\label{sec:pcp-example}
We introduce PCP by revising Milner's cyclic scheduler~\cite{milner89,dardhagay18}. Our PCP scheduler has exactly the same behaviour as the version presented in~\cref{sec:pgv-example}. We use $\pcp{\tm{\prod_{i}P_i}}$ to denote the parallel composition of the processes $\pcp{\tm{P_i}}$, and $\pcp{\plug{P}{Q}}$ to denote the plugging of $\pcp{\tm{Q}}$ in the one-hole process context $\pcp{\tm{P}}$:
\[
  \usingnamespace{pcp}
  \begin{array}{lrlr}
    \tm{\sched}
    & \defeq & \tm{\res{a_1}{a'_1}{\dots{\res{a_n}{a'_n}{}}}}
               \tm{\res{b_1}{b'_1}{\dots{\res{b_n}{b'_n}{}}}}
               \tm{\res{c_1}{c'_1}{\dots{\res{c_n}{c'_n}{}}}}
               \tm{\res{d}{d'}{}}
    \\ &     & \tm{(
               \ppar{\proc1}{\agent1}
               \parallel
               \prod_{2\leq{i}\leq{n}}(\ppar{\proc{i}}{\wait{c'_{i-1}}{\agent{i}}})
               )}
    \\
    \tm{\agent1}
    & \defeq & \tm{\close{a_i}{\wait{b_i}{\close{c_i}{\wait{c'_n}{\close{d}{\halt}}}}}}
    \\
    \tm{\agent{i}}
    & \defeq & \tm{\close{a_i}{\wait{b_i}{\close{c_i}{\halt}}}}
    \\
    \tm{\proc{i}}
    & \defeq & \tm{\wait{a'_i}{\plug{P_i}{\close{b'_i}{Q_i}}}}
  \end{array}
\]

\subsubsection*{Types}
Types $\pcp{\ty{A}}$, $\pcp{\ty{B}}$, $\pcp{\ty{C}}$ in PCP are based on classical linear logic propositions, and are defined by the following grammar:
\[
  \usingnamespace{pcp}
  \begin{array}{lcl}
    \ty{A}, \ty{B}, \ty{C}
    & \Coloneqq & \ty{\tytens[\cs{o}]{A}{B}}
      \sep        \ty{\typarr[\cs{o}]{A}{B}}
      \sep        \ty{\tyone[\cs{o}]}
      \sep        \ty{\tybot[\cs{o}]}
      \sep        \ty{\typlus[\cs{o}]{A}{B}}
      \sep        \ty{\tywith[\cs{o}]{A}{B}}
      \sep        \ty{\tynil[\cs{o}]}
      \sep        \ty{\tytop[\cs{o}]}
  \end{array}
\]
Each connective is annotated with a priority $\cs{o}\in\mathbb{N}$.
The types $\pcp{\ty{\tytens[\cs{o}]{A}{B}}}$ and $\pcp{\ty{\typarr[\cs{o}]{A}{B}}}$ type the endpoints of a channel over which we send or receive a channel of type $\pcp{\ty{A}}$, and then proceed as type $\pcp{\ty{B}}$. The types $\pcp{\ty{\tyone[\cs{o}]}}$ and $\pcp{\ty{{\tybot}[\cs{o}]}}$ type the endpoints of a channel whose session has terminated, and over which we send or receive a \emph{ping} before closing the channel. These two types act as units for $\pcp{\ty{\tytens[\cs{o}]{A}{B}}}$ and $\pcp{\ty{\typarr[\cs{o}]{A}{B}}}$, respectively.

@@

\subsubsection*{Environments}
Typing environments $\pcp{\ty{\Gamma}}$, $\pcp{\ty{\Delta}}$ associate names to types. Environments are linear, so two environments can only be combined as $\pcp{\ty{\Gamma}}, \pcp{\ty{\Delta}}$ if their names are distinct, \ie $\pcp{\fv(\ty{\Gamma})\cap\fv(\ty{\Delta})=\varnothing}$.
\[
  \usingnamespace{pcp}
  \begin{array}{lcl}
    \ty{\Gamma}, \ty{\Delta}
    & \Coloneqq & \ty{\emptyenv}
      \sep        \ty{\Gamma}, \tmty{x}{A}
  \end{array}
\]

@@

\subsubsection*{Terms}
We let $\pcp{\tm{P}}$, $\pcp{\tm{Q}}$ range over processes, produced by the following grammar.
\[
  \usingnamespace{pcp}
  \begin{array}[t]{lcl}
    \tm{P}, \tm{Q}
    & \Coloneqq & \tm{\link{x}{y}}
           \sep   \tm{\res{x}{y}{P}}
           \sep   \tm{(\ppar{P}{Q})}
           \sep   \tm{\halt}
    \\   & \sep & \tm{\send{x}{y}{P}}
           \sep   \tm{\close{x}{P}}
           \sep   \tm{\recv{x}{y}{P}}
           \sep   \tm{\wait{x}{P}}
    \\   & \sep & \tm{\inl{x}{P}}
           \sep   \tm{\inr{x}{P}}
           \sep   \tm{\offer{x}{P}{Q}}
           \sep   \tm{\absurd{x}}
  \end{array}
\]
The process $\pcp{\tm{\link{x}{y}}}$ links endpoints $\pcp{\tm{x}}$ and $\pcp{\tm{y}}$ and forwards communication from one to the other. $\pcp{\tm{\res{x}{y}{P}}}$, $\pcp{\tm{(\ppar{P}{Q})}}$ and $\pcp{\tm{\halt}}$ denote respectively the restriction processes where channel endpoints $\pcp{\tm{x}}$ and $\pcp{\tm{y}}$ are bound together and with scope $\pcp{\tm{P}}$, the parallel composition of processes $\pcp{\tm{P}}$ and $\pcp{\tm{Q}}$ and the terminated process.

Processes $\pcp{\tm{\send{x}{y}{P}}}$ and $\pcp{\tm{\recv{x}{y}{P}}}$ send or receive over channel $\pcp{\tm{x}}$ a value $\pcp{\tm{y}}$ and proceed as process $\pcp{\tm{P}}$. The processes $\pcp{\tm{\close{x}{P}}}$ and $\pcp{\tm{\wait{x}{P}}}$ send and receive an empty value---denoting the closure of channel $\pcp{\tm{x}}$, and continue as $\pcp{\tm{P}}$.

Processes $\pcp{\tm{\inl{x}{P}}}$ and $\pcp{\tm{\inr{x}{P}}}$ make a left and right choice, respectively and proceed as process $\pcp{\tm{P}}$. Dually, $\pcp{\tm{\offer{x}{P}{Q}}}$ offers both left and right branches, with continuations $\pcp{\tm{P}}$ and $\pcp{\tm{Q}}$, and $\pcp{\tm{\absurd{x}}}$ is the empty offer.

@@

\subsubsection*{Operational Semantics}
The operational semantics for PCP, given in \cref{fig:pcp-operational-semantics}, is defined as a reduction relation $\pcp{\red}$ on processes (bottom) and uses structural congruence (top). Each of the axioms of structural congruence corresponds to the axiom of the same name for PGV.\simon{Maybe worth highlighting that it is an internal mobility calculus, for the pi calculus people.}

@@

\subsubsection*{Translation}
The translation on types from PCP to PGV, $\ty{\cpgvT{\cdot}}$, is:
\[
  \begin{array}{lcl}
    \ty{\cpgvT{\pcp{\tytens[\cs{o}]{A}{B}}}}
    & = & \pgv{\ty{\tysend[\cs{o}]{\co{\cpgvT{A}}}{\cpgvT{B}}}}
    \\
    \ty{\cpgvT{\pcp{\typlus[\cs{o}]{A}{B}}}}
    & = & \pgv{\ty{\tyselect[\cs{o}]{\cpgvT{A}}{\cpgvT{B}}}}
  \end{array}
  \;
  \begin{array}{lcl}
    \ty{\cpgvT{\pcp{\tyone[\cs{o}]}}}
    & = & \ty{\pgv{\tyends[\cs{o}]}}
    \\
    \ty{\cpgvT{\pcp{\tynil[\cs{o}]}}}
    & = & \pgv{\ty{\tyselectemp[\cs{o}]}}
  \end{array}
  \;
  \begin{array}{lcl}
    \ty{\cpgvT{\pcp{\typarr[\cs{o}]{A}{B}}}}
    & = & \pgv{\ty{\tyrecv[\cs{o}]{\cpgvT{A}}{\cpgvT{B}}}}
    \\
    \ty{\cpgvT{\pcp{\tywith[\cs{o}]{A}{B}}}}
    & = & \pgv{\ty{\tyoffer[\cs{o}]{\cpgvT{A}}{\cpgvT{B}}}}
  \end{array}
  \;
  \begin{array}{lcl}
    \ty{\cpgvT{\pcp{\tybot[\cs{o}]}}}
    & = & \ty{\pgv{\tyendr[\cs{o}]}}
    \\
    \ty{\cpgvT{\pcp{\tytop[\cs{o}]}}}
    & = & \pgv{\ty{\tyofferemp[\cs{o}]}}
  \end{array}
\]
There are two separate translations on processes. The first, $\tm{\cpgvC{\cdot}}$, translates processes to \emph{configurations}. It translates as much as possible of the process to the corresponding configuration constructs. Once it hits the first action, it switches to the second translation, $\tm{\cpgvM{\cdot}}$, which translates processes to \emph{terms}:
\[
  \begin{array}{lcl}
    \pcp{\tm{\cpgvC{\res{x}{y}{P}}}}
    & = & \pgv{\tm{\res{x}{y}{\cpgvC{P}}}} \\
    \pcp{\tm{\cpgvC{\ppar{P}{Q}}}}
    & = & \pgv{\tm{\ppar{\cpgvC{P}}{\cpgvC{Q}}}} \\
    \pcp{\tm{\cpgvC{\send{x}{y}{P}}}}
    & = & \pgv{\tm{\res{y}{z}{(\child\;\letbind{x}{\send\;\pair{z}{x}}{\cpgvM{P}})}}} \\
    \pcp{\tm{\cpgvC{\inl{x}{P}}}}
    & = & \pgv{\tm{\res{y}{z}{(\child\;\letbind{x}{\andthen{\close\;(\send\;\pair{\inl{y}}{x})}{z}}{\cpgvM{P}})}}} \\
    \pcp{\tm{\cpgvC{\inr{x}{P}}}}
    & = & \pgv{\tm{\res{y}{z}{(\child\;\letbind{x}{\andthen{\close\;(\send\;\pair{\inr{y}}{x})}{z}}{\cpgvM{P}})}}} \\
    \pcp{\tm{\cpgvC{P}}}
    & = & \pgv{\tm{\child{\cpgvM{P}}}},\hfill\text{if none of the above apply}\\
    \\
    \pcp{\tm{\cpgvM{\link{x}{y}}}}
    & = & \pgv{\tm{\link\;{\pair{x}{y}}}} \\
    \pcp{\tm{\cpgvM{\res{x}{y}{P}}}}
    & = & \pgv{\tm{\letpair{x}{y}{\new}{\cpgvM{P}}}} \\
    \pcp{\tm{\cpgvM{\ppar{P}{Q}}}}
    & = & \pgv{\tm{\andthen{\spawn\;{(\lambda\unit.\cpgvM{P})}}{\cpgvM{Q}}}} \\
    \pcp{\tm{\cpgvM{\halt}}}
    & = & \pgv{\tm{\unit}} \\
    \pcp{\tm{\cpgvM{\close{x}{P}}}}
    & = & \pgv{\tm{\andthen{\close\;{x}}{\cpgvM{P}}}} \\
    \pcp{\tm{\cpgvM{\wait{x}{P}}}}
    & = & \pgv{\tm{\andthen{\wait\;{x}}{\cpgvM{P}}}} \\
    \pcp{\tm{\cpgvM{\send{x}{y}{P}}}}
    & = & \pgv{\tm{\letpair{y}{z}{\new}{\letbind{x}{\send\;{\pair{z}{x}}}{\cpgvM{P}}}}} \\
    \pcp{\tm{\cpgvM{\recv{x}{y}{P}}}}
    & = & \pgv{\tm{\letpair{y}{x}{\recv\;{x}}{\cpgvM{P}}}} \\
    \pcp{\tm{\cpgvM{\inl{x}{P}}}}
    & = & \pgv{\tm{\letbind{x}{\select{\labinl}\;{x}}{\cpgvM{P}}}} \\
    \pcp{\tm{\cpgvM{\inr{x}{P}}}}
    & = & \pgv{\tm{\letbind{x}{\select{\labinr}\;{x}}{\cpgvM{P}}}} \\
    \multicolumn{3}{l}{\pcp{\tm{\cpgvM{\offer{x}{P}{Q}}}}} \\
    & = & \pgv{\tm{\offer{x}{x}{\cpgvM{P}}{x}{\cpgvM{Q}}}} \\
    \pcp{\tm{\cpgvM{\absurd{x}}}}
    & = & \pgv{\tm{\offeremp{x}}}
  \end{array}
\]
The third, fourth, and fifth cases for $\tm{\cpgvC{\cdot}}$ translate the $\nu$-binders implicit in the encoding of bound sending to configuration constructs, which is required for completeness of the operational correspondence.
Typing environments are translated pointwise, and sequents $\pcp{\seq{P}{\ty{\Gamma}}}$ are translated as $\pgv{\cseq[\child]{\ty{\cpgvT{\ty{\Gamma}}}}{\cpgvC{P}}}$.

Recall our implementations of Milner's cyclic scheduler in PCP ($\pcp{\sched}$, \cref{sec:pcp-example}) and PGV ($\pgv{\sched}$, \cref{sec:pgv-example}). The translation of $\pcp{\sched}$ is exactly $\pgv{sched}$ where all processes are child processes.

\subsubsection*{Type preservation}
The translations $\tm{\cpgvC{\cdot}}$ and $\tm{\cpgvM{\cdot}}$ preserve typing along $\ty{\cpgvT{\cdot}}$:\simon{This reads weirdly---what's the intuition?}
\begin{restatablelemma}{lempcptopgvtermspreservation}[Preservation, $\cpgvM{\cdot}$]
  \label{lem:pcp-to-pgv-terms-preservation}
  \hfill\\%newline before theorem statement
  If $\pcp{\seq{P}{\ty{\Gamma}}}$ in PCP,
  then $\pgv{\tseq[\cs{p}]{\ty{\cpgvT{\Gamma}}}{\cpgvM{P}}{\tyunit}}$ in PGV.
\end{restatablelemma}
\begin{proof}
  By induction on the derivation of $\pcp{\seq{P}{\ty{\Gamma}}}$.
  Details in \cref{prf:lem-pcp-to-pgv-terms-preservation}.
\end{proof}
\begin{restatabletheorem}{thmpcptopgvconfspreservation}[Preservation, $\cpgvC{\cdot}$]
  \label{thm:pcp-to-pgv-confs-preservation}
  \hfill\\%newline before theorem statement
  If $\pcp{\seq{P}{\ty{\Gamma}}}$ in PCP,
  then $\pgv{\cseq[\child]{\ty{\cpgvT{\Gamma}}}{\cpgvC{P}}}$ in PGV.
\end{restatabletheorem}
\begin{proof}
  By induction on the derivation of $\pcp{\seq{P}{\ty{\Gamma}}}$.
  Details in \cref{prf:lem-pcp-to-pgv-terms-preservation}.
\end{proof}

@@

@@

\begin{restatabletheorem}{thmpcptopgvoperationalcorrespondencesoundness}%
  [Operational Correspondence, Soundness, $\cpgvC{\cdot}$]
  \label{thm:pcp-to-pgv-operational-correspondence-soundness}
  \hfill\\%newline before theorem statement
  If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pgv{\tm{\cpgvC{P}}\cred\tm{\conf{C}}}$,
  there exists a $\tm{Q}$ such that $\pcp{\tm{P}\red^+\tm{Q}}$ and $\pgv{\tm{\conf{C}}\cred^\star\tm{\cpgvC{Q}}}$
\end{restatabletheorem}
\begin{proof}
  By induction on the derivation of $\pgv{\tm{\cpgvC{P}}\cred\tm{\conf{C}}}$.\simon{Surprising that you can get it by the derivation of the reduction relation---normally, 'soundness' would be proved by shunting into a canonical form and then proceeding by induction the structure of the term / induction on typing derivations.}
  Details in \cref{prf:thm-pcp-to-pgv-operational-correspondence-soundness}.
\end{proof}
